---
title: "HW2"
output: html_document
date: '2022-04-19'
---

```{r setup, include=FALSE}
df = ak91
yrs_educ <- df$YRS_EDUC
wkly_wage <- df$WKLY_WAGE
#College Grads
has_college_degree <- yrs_educ == 16

```


```{r cars}
#A)
x_estimator = (1 / 329509) * sum(has_college_degree)
x_estimator
```
# The estimate for P(X=1) is about 0.1084857


```{r pressure, echo=FALSE}
#B)
num = 0
denom = 0
for (x in 1:329509){
  denom = denom + has_college_degree[x]
  num = num + (has_college_degree[x] * wkly_wage[x])
}

mu_college = num / denom
mu_college
```
#The number is about 594.4866
```{r cars}
#C)
se_college = (1/ (sqrt(329509))) *  sqrt(mu_college/x_estimator)
se_college

```
#The standard error is about 0.1289589
```{r cars}
#D)
conf_int = c(mu_college - (1.96 * se_college), mu_college + (1.96 * se_college))
conf_int

```
#The Confidence Interval is: [594.2338 , 594.7393]

#E)
The value 600 for the Null Hypothesis is not in the confidence interval listed above. At a 5% significance level, this would be statistically significant and imply E[Y|X=1] != 600, so we reject the null hyp. This implies that the likelihood that the average weekly wage for those with degrees in the sample is 600 given other conditions is less that 5%.

#F)
595 is also not within the confidence interval, which would imply that we should also reject the null hypothesis.
This implies that the likelihood that the average weekly wage for those with degrees in the sample is 595 given other conditions is less that 5%.


#Extra Credit
```{r cars}
#A)
my_confint <- function(mu_hat , se , alpha) {
  z_val = qnorm(1-(alpha/2))

  confint <- c(mu_hat - (z_val * se) , mu_hat + (z_val * se))
  return (confint)
}
```


```{r cars}
#B)
my_testrejects <- function(confint , mu_0) {
  is_in_confint <- (mu_0 - confint[1] >= 0) & (confint[2] - mu_0 >= 0)
  is_rejected <- !is_in_confint
  return(is_rejected)
}
confint_01 <- my_confint(mu_college , se_college , 0.01)
my_testrejects(confint_01, 600)
confint_10 <- my_confint(mu_college , se_college , 0.1)
my_testrejects(confint_10, 600)
```
#There appears to be an error with my SE_College since the first one rejects as well
```{r cars}
#C)
my_twosidedtest <- function(mu_hat , se , alpha , mu_0) {
  is_rejected <-   my_testrejects(my_confint(mu_hat , se , alpha), mu_0)
  if (is_rejected) {
    message <- "REJECTS the NULL"
  }
  else{
    message <- "FAILS to REJECT the NULL"
  }
  print(message)
}

my_twosidedtest(mu_college , se_college , 0.01, 600)
my_twosidedtest(mu_college , se_college , 0.10, 600)
```